---
title: "R for Data Analysis Notebook"
output: html_notebook
---
# 3. Data Visualisation

```{r}
library(tidyverse)

```
```{r}
mpg
```
```{r}
ggplot(mpg)+geom_point(mapping = aes(x=displ,y=hwy))
```

### ggplot will always look like this:
ggplot(data = <DATA>) + 
  <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))
  
## 3.2.4
Run ggplot(data = mpg)  what do you see?
Nothing

How many rows in mpg?  columns?
```{r}
dim(mpg)
```

What does drv varable describe?  Read the help
?mpg

front or rear wheel drive

 Make a scatterplot of hwy vs cyl.
```{r}

 ggplot(mpg)+geom_point(aes(x=hwy, y = cyl))
```
 



make a plot of class v drv
```{r}
ggplot(mpg) + geom_point(aes(x= class,y=drv))
```



```{r}
ggplot(mpg)+geom_point(aes(x=displ,y=hwy,color=class))
```
```{r}
ggplot(mpg)+geom_point(aes(x=displ,y=hwy,alpha = class))
```


```{r}
ggplot(mpg)+geom_point(aes(x=displ,y=hwy,shape = class))
```


```{r}
ggplot(mpg)+geom_point(aes(x=displ,y=hwy),color = "blue")

```


```{r}
ggplot(mpg)+geom_point(mapping = aes(displ,hwy,colour = displ < 5))
```

```{r}
ggplot(mpg)+geom_point(aes(displ,hwy))+
  facet_wrap(~class)
```

Try different GEOMS

```{r}
ggplot(mpg)+geom_smooth(aes(displ,hwy))
```

```{r}
ggplot(mpg)+geom_smooth(aes(displ,hwy,linetype = drv))
```

Multiple geoms on the same plot!

```{r}
ggplot(mpg)+
  geom_point(aes(displ,hwy))+
  geom_smooth(aes(displ,hwy))
```
Now - add the mapping to the ggplot() function and that will carry over to any geom that you add!

```{r}
ggplot(mpg,aes(displ,hwy))+
  geom_smooth()+
  geom_line()+
  geom_point()
```

tests and trials
```{r}
ggplot(mpg,aes(displ,hwy))+
  geom_point(size=3)+
  geom_smooth(se=FALSE)
```
```{r}
ggplot(mpg,aes(displ,hwy))+
  geom_point(size = 4)+
  geom_smooth(aes(linetype = drv),se=FALSE)
```

```{r}
ggplot(mpg,aes(displ,hwy,color=drv))+
  geom_point(size=3)+
  geom_smooth(se=FALSE)
```

```{r}
ggplot(mpg,aes(displ,hwy)) +
  geom_point(aes(color=drv))+
  geom_smooth(se=FALSE)
```


```{r}
ggplot(mpg,aes(displ,hwy)) +
  geom_point(aes(color=drv))+
  geom_smooth(se=FALSE,aes(linetype=drv))
```



ggplot(data = <DATA>) + 
  <GEOM_FUNCTION>(
     mapping = aes(<MAPPINGS>),
     stat = <STAT>, 
     position = <POSITION>
  ) +
  <COORDINATE_FUNCTION> +
  <FACET_FUNCTION>








































































